---
title: "Effective Giving AI Persuasion Project - Complete Analysis Report"
author: "Josh White"
date: 31 August 2025
format:
  html:
    toc: true
    toc-depth: 3
    df_print: paged
    code-fold: true
    code-tools: true
    code-link: true
    self-contained: true
    theme: flatly
    linestretch: 1
    fig-width: 7.085
    fig-height: 5
    fig-dpi: 300
    fig-cap: true
  pdf:
    pdf-engine: xelatex
    toc: true
    number-sections: true
    df_print: kable
    fig-align: center
    fig-width: 7.085
    fig-height: 5
    fig-cap: true
    fontsize: 9pt
    monofont: 'Source Code Pro'
    monofontoptions: 
    - Scale=0.666
#. Following allows for code and output to be wrapped .#
    include-in-header: 
       text: |
         \usepackage{fvextra}
         \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
    include-before-body:
      text: |
        \RecustomVerbatimEnvironment{verbatim}{Verbatim}{
          showspaces = false,
          showtabs = false,
          breaksymbolleft={},
          breaklines
          % Note: setting commandchars=\\\{\} here will cause an error 
        }
execute:
  echo: true
  warning: false
  message: false
params:
  include_code: true
---

```{r}
#| label: setup
#| include: false

# attach main packages
# Imports, called via ::
# Suggests, not used
desc <- desc::desc(file = "DESCRIPTION")
deps <- desc$get_deps()
pkgs <- deps$package[deps$type == "Depends" & deps$package != "R"]
invisible(lapply(pkgs, require, character.only = TRUE))

# Download data if needed
if (!dir.exists("data") || length(list.files("data")) == 0) {
  source("scripts/download_data.R")
  download_osf_data_dir("6ya5n")
}

# Load config (sets global vars used throughout analysis)
source("scripts/config.R")

# Load functions used for analysis
source("scripts/functions/heterogeneity_functions.R")
source("scripts/functions/agreement_functions.R")
source("scripts/functions/pcs_hierarchy_functions.R")
source("scripts/functions/gam_functions.R")
source("scripts/functions/causal_forest_functions.R")
source("scripts/functions/statistical_helpers.R")

# Create output directories if they don't exist
fs::dir_create("output", "figures")

# Override echo setting based on parameter
knitr::opts_chunk$set(echo = params$include_code)
```

# Introduction

This report presents the complete analysis for the Effective Giving AI Persuasion Project. The analysis examines the effectiveness of AI-powered persuasive conversations compared to static messages and control conditions in promoting charitable giving to effective charities.

## Project Overview

The study investigates whether AI-powered conversations can be more persuasive than static messages in encouraging donations to effective charities like the Against Malaria Foundation (AMF). The analysis includes:

- Sample descriptives and attrition analysis
- Average Treatment Effects (ATEs)
- Heterogeneity analysis using causal forests
- Persuasive strategy analysis
- AI accuracy assessment
- Comprehensive visualizations

# Data and Setup

```{r}
#| label: data_setup

# Data is automatically downloaded during setup
# You can also manually download using:
# download_osf_data("6ya5n")
```

# Sample Descriptives and Attrition Analysis

## Attrition Analysis

```{r}
#| file: scripts/analysis/attrition.R
#| label: attrition
```

## Sample Characteristics

```{r}
#| file: scripts/analysis/sample_descriptives.R
#| label: sample_descriptives
```


# Charity Descriptives

```{r}
#| file: scripts/analysis/charity_descriptives.R
#| label: charity_descriptives
```

# Motivation Analysis

```{r}
#| file: scripts/analysis/motivation_analysis.R
#| label: motivation_analysis
```

# Average Treatment Effects (ATEs)

```{r}
#| file: scripts/analysis/ates.R
#| label: ates
```

# Categorical Heterogeneity Analysis

```{r}
#| file: scripts/analysis/cat_heterogeneity.R
#| label: cat_heterogeneity
```

# Causal Forest Analysis

```{r}
#| file: scripts/analysis/causal_forest.R
#| label: causal_forest
```

# Generalized Additive Models (GAMs)

```{r}
#| file: scripts/analysis/gams.R
#| label: gams
```

# Persuasive Strategies Analysis

```{r}
#| file: scripts/analysis/persuasive_strategies.R
#| label: persuasive_strategies
```

# AI Accuracy Assessment

```{r}
#| file: scripts/analysis/ai_accuracy.R
#| label: ai_accuracy
```

# Figures

## Charity Descriptive Plot

```{r}
#| file: scripts/figures/charity_descriptive_plot.R
#| label: charity_plot
#| fig-cap: "Figure 2: Charity descriptive statistics"
#| fig-height: 7.1
```

## Motivation Plots

```{r}
#| file: scripts/figures/motivation_plots.R
#| label: motivation_plots
#| fig-cap: "Figure S1: Motivation analysis plots"
#| fig-height: 3.5
```

## Main Treatment Effects Plot

```{r}
#| file: scripts/figures/main_plot.R
#| label: main_plot
#| fig-cap: "Figure 3: Main treatment effects"
#| fig-height: 3
```

## Categorical Heterogeneity Plot

```{r}
#| file: scripts/figures/cat_het_plot_cates.R
#| label: cat_het_plot
#| fig-cap: "Figure 4: Categorical heterogeneity in treatment effects"
#| fig-height: 3.5
```

## Binned Heterogeneity Plot

```{r}
#| file: scripts/figures/binned_het_cates.R
#| label: binned_het_plot
#| fig-cap: "Figure S2: Binned heterogeneity analysis"
#| fig-height: 6
```

## VIP and GAM Plot

```{r}
#| file: scripts/figures/vip_and_gam_plot.R
#| label: vip_gam_plot
#| fig-cap: "Figure 5: Variable importance and GAM analysis"
#| fig-height: 6
```

## Causal Forest Plots

```{r}
#| file: scripts/figures/causal_forest_plots.R
#| label: causal_forest_plots
#| fig-cap: "Figures S3 and S4: Partial dependence plots and unadjusted heterogeneity plots"
#| fig-height: 9.3
```

## Strategy Plot

```{r}
#| file: scripts/figures/strategy_plot.R
#| label: strategy_plot
#| fig-cap: "Figure 6: Persuasive strategies analysis"
#| fig-height: 7
```

## Accuracy Figure

```{r}
#| file: scripts/figures/accuracy_figure.R
#| label: accuracy_figure
#| fig-cap: "Figure S5: AI accuracy assessment"
#| fig-height: 4
```

# Tables

## GAM Tables

```{r}
#| file: scripts/tables/gam_tables.R
#| label: gam_tables
```

## Strategy Regression Table

```{r}
#| file: scripts/tables/strategy_regression_table.R
#| label: strategy_table
```

# Session Information

```{r}
#| label: session_info
#| echo: true

sessionInfo()
```

# Appendix

## Additional Notes

- All figures are saved in the `output/figures/` directory
- Raw data and processed datasets are available in the `data/` directory
- Python scripts for NLP processing are located in `scripts/nlp/`
- This report can be generated with or without code chunks using the `include_code` parameter

